---
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

## Ivan Setiawan
## Developing Data Products 
## February 21st, 2015

-------------------------

## Presentation Layout

1. Project Introduction

2. Sidebar Panel and Main Panel Explanation

3. Summary of World Phone Data

4. Interactive Chart 

5. Conclusion

---------------------

## Project Introduction

 1. This is a simple project about the world phone adoption from 1951-1961 
 2. The data is already pre-loaded inside the R studio
 3. The presentation includes all of the histogram representation of world phone based on region
 4. The user can select the region from the drop down menu
 5. The user then can select the color of the histogram from the radio button
 6. The data presentation is separated into three tabs: data summary, data table, and the histogram
 7. Finally, there is a function to download the histogram either in PDF or PNG format

---

## Sidebar Panel and Main Panel

1. The sidebar panel consists of drop down menu to select the region
2. Radio buttons are then added in order to select the color and the download format
3. The main panel are created in the tab format to give more user interface experiences regarding the data
4. The Summary tab contains all of the information regarding min and max value, median, mean, and 1st and 3rd percentile
5. The Show Data Table tab contains all of the data table information
6. The Show Histogram Tab contains the data representation using the reactive function

------------------------------------

### World Phone Data Summary

```{r}
summary(WorldPhones)
```

--------------------------------------

### Interactive Chart

```{r echo = FALSE, cache=FALSE}
shinyApp(
  
  ui = fluidPage(
    selectInput("region", "Region:", 
                choices = colnames(WorldPhones)),
    plotOutput("phonePlot")
  ),
  
  server = function(input, output) {
    output$phonePlot <- renderPlot({
      barplot(WorldPhones[,input$region]*1000, 
              ylab = "Number of Telephones", xlab = "Year")
    })
  },
  
  options = list(height = 500)
)
```
--------------------------

### Conclusion

1. This documentation gives idea how the World Phone Data apps works
2. Based on the observation, Africa and Oceania had the least phone usage adoption that might be because of lack infrastructure in early days
3. In comparison, North America and Europe had the fastest phone usage adoption